Figures

### 2016-08-12 case_study_mpa/3_mpa_spp_analysis.Rmd
cleaning up plots

### Plot the bar chart
barchart_mpa_gap <- ggplot(mpa_all_runs1, 
                           aes(x = trial, fill = cat, weight = p_cat)) +
  ggtheme_plot + 
  theme(panel.grid.major.y = element_blank()) +
  geom_bar(stat = 'count', alpha = .8) +
  scale_fill_manual(values = c('>10%'  = '#4dac26', 
                               '5-10%' = '#b8e186', 
                               '2-5%'  = '#fbe5c5', 
                               '0-2%'  = '#f1b6da',
                               'gap'   = '#d01c8b')) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 125), breaks = c(seq(0, 100, 20))) +
  geom_text(aes(label = sprintf('n = %s', n_trial), y = 101), hjust = 0, 
            size = 2, 
            color = 'grey30') +
  scale_x_discrete(labels = c('5. IUCN 2015',
                              '4. AM 2015 (0%) +\nIUCN 2015', 
                              '3. AM 2015 (0%)', 
                              '2. AM 2015 (50%)', 
                              '1. AM 2014 (50%)')) +
  coord_flip() +
  labs(x = 'Scenario', 
       y = 'Percent of species by MPA coverage', 
       fill = 'MPA coverage')

>>>>

break_nums <- seq(0, 100, 20)

### Plot the bar chart
barchart_mpa_gap <- ggplot(mpa_all_runs1, 
                           aes(x = trial, fill = cat, weight = p_cat)) +
  ggtheme_plot + 
  theme(panel.grid.major.y = element_blank()) +
  geom_bar(stat = 'count', alpha = 1) +
  scale_fill_manual(values = c('>10%'  = '#4dac26', 
                               '5-10%' = '#b8e186', 
                               '2-5%'  = '#fbe5c5', 
                               '0-2%'  = '#f1b6da',
                               'gap'   = '#d01c8b')) +
  ### add grid lines; horizontal but then get flipped
  geom_hline(yintercept = break_nums, size = 0.25, color = 'white', alpha = .5) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 125), breaks = break_nums,
                     labels = sprintf('%s%%', break_nums)) + 
  geom_text(aes(label = sprintf('n = %s', n_trial), y = 101), hjust = 0, 
            size = 2, 
            color = 'grey30') +
  scale_x_discrete(labels = c('5. IUCN 2015',
                              '4. AM 2015 (0%) +\nIUCN 2015', 
                              '3. AM 2015 (0%)', 
                              '2. AM 2015 (50%)', 
                              '1. AM 2014 (50%)')) +
  coord_flip() +
  labs(x = 'Scenario', 
       y = 'Percent of species by MPA coverage', 
       fill = 'MPA coverage')

### 2016-08-12 case_study_ohi/ohi_paired_maps.Rmd
cleaning up plots

if(basename(getwd()) != 'data_explore') setwd('data_explore')
source('data_explore_fxns.R')
### When knitting this, it automatically sets WD to be this directory...
### the 'setwd()' is there for running by chunk
```

@@

#   theme(text = element_text(family = 'Helvetica', color = 'gray30', size = 12),
#         plot.title = element_text(size = rel(1.5), hjust = 0, face = 'bold'),
#         legend.position = 'none') +
  geom_hline(yintercept = 0, color = 'gray50', size = .5) +
  geom_violin(fill = 'grey80', alpha = .5,
              draw_quantiles = c(.25, .5, .75)) +
  geom_point(position = position_jitter(w = .3), 
             color = '#4d4dac', alpha = .5) +
  geom_violin(fill = NA, draw_quantiles = c(.25, .5, .75)) +
  labs(x = 'Scenario',
       y = 'Change in SPP status') +
  scale_x_discrete(labels = c('1. AquaMaps \n(40% threshold)', 
                              '2. AquaMaps \n(no threshold)', 
                              '3. AquaMaps \n(40% -> no threshold)'))

print(bplot_abs)
ggsave(file.path(dir_fig, 'fig3_boxplot2_abs_diff.png'),
       height = 4.5, width = 8.7, units = 'cm', dpi = 600)
ggsave(file.path(dir_fig, 'fig3_boxplot2_abs_diff.tif'), device = 'tiff',
       height = 4.5, width = 8.7, units = 'cm', dpi = 600)

>>>>

source('~/github/IUCN-AquaMaps/data_explore/data_explore_fxns.R')

@@

  geom_hline(yintercept = 0, color = 'gray50', size = .5) +
  geom_violin(fill = 'grey80', alpha = .5,
              scale = 'width',
              draw_quantiles = c(.25, .5, .75)) +
  geom_point(position = position_jitter(w = .3), 
             color = 'black', alpha = 1, size = 0.25) +
  geom_violin(fill = NA, 
              draw_quantiles = c(.25, .5, .75),
              scale = 'width') +
  labs(x = 'Scenario',
       y = 'Change in SPP status') +
  scale_x_discrete(labels = c('1. AquaMaps \n(40% threshold)', 
                              '2. AquaMaps \n(no threshold)', 
                              '3. AquaMaps \n(40% -> no threshold)'))

print(bplot_abs)
ggsave(file.path(dir_fig, 'fig3a_boxplot_paired_maps.png'),
       height = 4.5, width = 8.7, units = 'cm', dpi = 600)
ggsave(file.path(dir_fig, 'fig3a_boxplot_paired_maps.tif'), device = 'tiff',
       height = 4.5, width = 8.7, units = 'cm', dpi = 600)

### 2016-08-12 coralmaps/coral_maps.Rmd
cleaning up plots

break_nums <- seq(0, 100, 20)
coral_area_plot <- ggplot(spp_coral_clip2, aes(x = l_to_h, y = pct_value, fill = depth)) +
  ggtheme_plot +
  # geom_linerange(aes(ymin = kept_ratio, ymax = 100),
  #                position = position_dodge(width = 0.5)) +
  geom_area() +
  scale_fill_manual(values = c('0 - 200 m' = 'grey90', '200 m +' = 'grey10')) +
  geom_hline(yintercept = break_nums, color = 'white', size = .25) +
  scale_y_continuous(# limits = c(0, 100), ### why is this causing a vertical line?
                     breaks = break_nums,
                     labels = paste0(break_nums, '%')) +
  # scale_x_discrete(labels = element_blank()) +
  # theme(axis.title.x = element_blank()) +
  labs(y = 'IUCN % of coral range',
       x = 'Count of coral species')
print(coral_area_plot)

>>>>

break_nums <- seq(0, 100, 20)
num_spp <- max(spp_coral_clip2$l_to_h)
coral_area_plot <- ggplot(spp_coral_clip2, aes(x = l_to_h, y = pct_value, fill = depth)) +
  ggtheme_plot +
  geom_area(show.legend = FALSE) +
  scale_fill_manual(values = c('0 - 200 m' = 'grey90', '200 m +' = 'grey10')) +
  geom_hline(yintercept = break_nums, color = 'white', size = .25) +
  annotate("text", x = (num_spp - 10), y = 95, hjust = 1, vjust = .5, size = 3, color = 'white', 
           fontface = 'bold.italic', label = "200 m and deeper") + 
  annotate("text", x = 10, y = 5, hjust = 0, vjust = .5, size = 3, color = 'grey10', 
           fontface = 'bold.italic', label = "0 - 200 m") + 
  scale_y_continuous(# limits = c(0, 100), ### why is this causing a vertical line?
                     breaks = break_nums,
                     labels = paste0(break_nums, '%')) +
  scale_x_continuous(limits = c(0, num_spp), ### why is this causing a vertical line?
                     breaks = c(seq(0, 400, 100), num_spp)) +
  labs(y = 'IUCN % of coral range',
       x = 'Count of IUCN coral species maps')
print(coral_area_plot)

### 2016-08-12 data_explore/data_explore.Rmd
cleaning up plots

``` {r plot bar charts by taxa, echo = FALSE, message = FALSE, warning = FALSE, eval = TRUE}
### bar charts comparing number of species in each class for each data set

#library(colorspace)
#hclvec <- heat_hcl(3); colvec <- c('AquaMaps' = hclvec[1], 'Both' = hclvec[2], 'IUCN' = hclvec[3])
#colvec <- c('AquaMaps' = '#1b9e77', 'Both' = '#565080', 'IUCN' = '#d95f02')
colvec <- c('AquaMaps' = '#76A94C', 'Both' = '#e18258', 'IUCN' = '#9168a9')

taxa_df_long <- taxa_df %>%
  dplyr::select(class, AquaMaps = n_am_class_solo, IUCN = n_iucn_class_solo, Both = n_class_both) %>%
  gather(dataset, n_spp, AquaMaps:Both) %>%
  group_by(class) %>%
  mutate(n_total = sum(n_spp, na.rm = TRUE),
         percent = n_spp/n_total * 100,
         dataset = factor(dataset, levels = c('AquaMaps', 'Both', 'IUCN'), ordered = TRUE)) %>%
  arrange(desc(dataset))

bar_taxa <- ggplot(taxa_df_long, aes(x = class, y = percent, fill = dataset)) +
  ggtheme_plot + 
  theme(panel.grid.major.x = element_blank()) +
  geom_bar(stat = 'identity', alpha = 1) +
  geom_hline(yintercept = break_nums, size = 0.25, color = 'white', alpha = .5) +
  scale_fill_manual(values = colvec) +
  geom_text(aes(label = sprintf('n = %s', n_total), y = 102), 
            size = 2, 
            angle = 90, hjust = 0, color = 'grey30') +
  theme(axis.text.x = element_text(angle = 75, hjust = 1)) + 
  scale_y_continuous(expand = c(0, 0), 
                     limits = c(0, 130),
                     breaks = break_nums,
                     labels = sprintf('%s%%', break_nums)) + 
  labs(# title = 'Species maps by taxonomic class',
       x = 'Class', 
       y = 'Percent of mapped species',
       fill = 'Dataset')

print(bar_taxa)
ggsave(filename = file.path(dir_fig, 'bar_by_taxa_all.png'), 
       width = 17.8, height = 7, units = 'cm', dpi = 600)

@@

![](../figures/bar_by_taxa_all.png)

``` {r plot bar-line charts by taxa, echo = FALSE, message = FALSE, warning = FALSE, eval = TRUE}
### bar charts comparing number of species in each class for each data set

#library(colorspace)
#hclvec <- heat_hcl(3); colvec <- c('AquaMaps' = hclvec[1], 'Both' = hclvec[2], 'IUCN' = hclvec[3])
#colvec <- c('AquaMaps' = '#1b9e77', 'Both' = '#565080', 'IUCN' = '#d95f02')
colvec <- c('AquaMaps' = '#76A94C', 'Both' = '#e18258', 'IUCN' = '#9168a9')

@@

bar_taxa <- ggplot(taxa_df2, aes(x = class, color = dataset)) +
  ggtheme_plot + 
  theme(panel.grid.major.x = element_blank()) +
  geom_linerange(aes(ymin = start, ymax = end, size = dataset),
                 position = position_dodge(width = 0.5)) +
  scale_size_manual(values = c('IUCN' = .25, 'AquaMaps' = .25, 'Both' = 2.5)) +
  scale_color_manual(values = c('IUCN' = 'black', 'AquaMaps' = 'grey60', 'Both' = 'black')) +
  geom_text(aes(label = n_label, y = 102),
            size = 2,
            angle = 90, hjust = 0, color = 'grey30') +
  theme(axis.text.x = element_text(angle = 75, hjust = 1)) +
  scale_y_continuous(expand = c(0, 0),
                     limits = c(0, 130),
                     breaks = break_nums,
                     labels = sprintf('%s%%', break_nums)) +
  labs(# title = 'Species maps by taxonomic class',
       x = 'Class',
       y = 'Percent of mapped species',
       fill = 'Dataset')

print(bar_taxa)
ggsave(filename = file.path(dir_fig, 'bar2_by_taxa_all.png'), 
       width = 17.8, height = 7, units = 'cm', dpi = 600)

@@

ggsave(file.path(dir_fig, 'scatter_quadmap.png'),
       width = 17.8, height = 9, units = 'cm', dpi = 600)

@@

# print(barchart_spp_gp_quads)
ggsave(plot = barchart_spp_gp_quads,
       filename = file.path(dir_fig, 'barchart_spp_gp_quads.png'),
       width = 17.8, height = 7, units = 'cm', dpi = 600)

>>>>

``` {r plot_bar_charts_by_taxa_old, echo = FALSE, message = FALSE, warning = FALSE, eval = FALSE}
# ### bar charts comparing number of species in each class for each data set
# 
# #library(colorspace)
# #hclvec <- heat_hcl(3); colvec <- c('AquaMaps' = hclvec[1], 'Both' = hclvec[2], 'IUCN' = hclvec[3])
# #colvec <- c('AquaMaps' = '#1b9e77', 'Both' = '#565080', 'IUCN' = '#d95f02')
# colvec <- c('AquaMaps' = '#76A94C', 'Both' = '#e18258', 'IUCN' = '#9168a9')
# 
# taxa_df_long <- taxa_df %>%
#   dplyr::select(class, AquaMaps = n_am_class_solo, IUCN = n_iucn_class_solo, Both = n_class_both) %>%
#   gather(dataset, n_spp, AquaMaps:Both) %>%
#   group_by(class) %>%
#   mutate(n_total = sum(n_spp, na.rm = TRUE),
#          percent = n_spp/n_total * 100,
#          dataset = factor(dataset, levels = c('AquaMaps', 'Both', 'IUCN'), ordered = TRUE)) %>%
#   arrange(desc(dataset))
# 
# break_nums <- seq(0, 100, 20)
# 
# bar_taxa <- ggplot(taxa_df_long, aes(x = class, y = percent, fill = dataset)) +
#   ggtheme_plot + 
#   theme(panel.grid.major.x = element_blank()) +
#   geom_bar(stat = 'identity', alpha = 1) +
#   geom_hline(yintercept = break_nums, size = 0.25, color = 'white', alpha = .5) +
#   scale_fill_manual(values = colvec) +
#   geom_text(aes(label = sprintf('n = %s', n_total), y = 102), 
#             size = 2, 
#             angle = 90, hjust = 0, color = 'grey30') +
#   theme(axis.text.x = element_text(angle = 75, hjust = 1)) + 
#   scale_y_continuous(expand = c(0, 0), 
#                      limits = c(0, 130),
#                      breaks = break_nums,
#                      labels = sprintf('%s%%', break_nums)) + 
#   labs(# title = 'Species maps by taxonomic class',
#        x = 'Class', 
#        y = 'Percent of mapped species',
#        fill = 'Dataset')
# 
# print(bar_taxa)
# ggsave(filename = file.path(dir_fig, 'fig1a_bar_by_taxa_all.png'), 
#        width = 17.8, height = 7, units = 'cm', dpi = 600)

@@

``` {r plot_barline_charts_by_taxa, echo = FALSE, message = FALSE, warning = FALSE, eval = TRUE}
### bar charts comparing number of species in each class for each data set

@@

bar_taxa <- ggplot(taxa_df2, aes(x = class, color = dataset)) +
  ggtheme_plot + 
  theme(panel.grid.major.x = element_blank()) +
  geom_linerange(aes(ymin = start, ymax = end, size = dataset),
                 position = position_dodge(width = 0.5)) +
  scale_size_manual(values = c('IUCN' = .25, 'AquaMaps' = .25, 'Both' = 2.5)) +
  scale_color_manual(values = c('IUCN' = 'black', 'AquaMaps' = 'grey60', 'Both' = 'black')) +
  geom_text(aes(label = n_label, y = 102),
            size = 2,
            angle = 90, hjust = 0, color = 'grey30') +
  theme(axis.text.x = element_text(angle = 75, hjust = 1)) +
  scale_y_continuous(expand = c(0, 0),
                     limits = c(0, 130),
                     breaks = break_nums,
                     labels = sprintf('%s%%', break_nums)) +
  labs(x = 'Class',
       y = 'Percent of mapped species',
       fill = 'Dataset')

print(bar_taxa)
ggsave(filename = file.path(dir_fig, 'fig1a_bar_by_taxa_all.png'), 
       width = 17.8, height = 7, units = 'cm', dpi = 600)

@@

ggsave(file.path(dir_fig, 'fig2a_scatter_quadmap.png'),
       width = 17.8, height = 9, units = 'cm', dpi = 600)

@@

print(barchart_spp_gp_quads)

ggsave(plot = barchart_spp_gp_quads,
       filename = file.path(dir_fig, 'fig2b_barchart_spp_gp_quads.png'),
       width = 17.8, height = 7, units = 'cm', dpi = 600)

### 2016-08-12 ms_figures.Rmd
cleaning up plots

---
title: "Figures"
output:
  word_document: default
  pdf_document:
    number_sections: no
    toc: no
  html_document:
    highlight: haddock
    number_sections: no
    theme: spacelab
    toc: no
---

@@

@@

>>>>

---
title: "Figures"
output:
  html_document:
    highlight: haddock
    number_sections: no
    theme: spacelab
    toc: no
  pdf_document:
    number_sections: no
    toc: no
  word_document: default
---

@@

![Change in MPA coverage](figures/bar2_by_taxa_all.png)

@@

### New figures - corals

![Change in MPA coverage](figures/coral_area_plot.png)

![Change in MPA coverage](figures/scatter_quadmap_corals.png)
